A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer

### 2011-01-21 paper.tex
add gestures family pic
Add Gilles notes

\documentclass{llncs}
%
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}

@@

\newcommand{\image}[3]{\imagepathext{#1}{FIGURES}{#2}{eps}{#3}}
\newcommand{\png}[2]{\imagepathext{width=\columnwidth}{pics}{#1}{png}{#2}}

@@

Testing Refrences \cite{Gesturecraft} and \cite{skinColorSeg}.

\section{Gesture recognition}
First definition of gestures come from the interaction between two human in a discussion, these type of gestures is used to add more precision on the details and according to recent paper, is made by the same mental region of the speech []. An extended meaning come also from gestures language for dumb people.
Gesture recognition got the attention of HCI researchers in order to find better ways to talk to the computer. The first one was the Hand Gestural Cursor (Put-That-There[]) aiming to the simplification of the means of communication between human and the machine.
Since then, the gesture definition included more techniques and got applied on the 2D recognition which is the multi-touch gestures.

@@

\section{Gestures in Talk-shows}
We have analyzed some talk-shows in order to extract important gestures being performed.
(Get the Study from the report + pics + refs)

@@

@@

\subsection{Blob Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper.

When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.

To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.

@@

\section{Simplified gesture generation}
Using these blocks we are able to perturb

@@

\section{Usability analysis and tests}

>>>>

\documentclass{llncs}
%
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps}

@@

\newcommand{\image}[3]{\imagepathext{#1}{pics}{#2}{eps}{#3}}
\newcommand{\png}[2]{\imagepathext{width=\columnwidth}{pics}{#1}{png}{#2}}

@@

We present in this paper an approach that could allow the detection and the interpretation of gestures of a TV spectator from a simple and low cost camera. 
The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presentator or actor [RevTV]

ref \cite{Gesturecraft} and \cite{skinColorSeg}.

\section{Gesture Semantics and Recognition}
Semantics of gestures has been studied when analysing the interaction of a user explaining a story. 
First definition of gestures come from the interaction between two human in a discussion, these type of gestures is used to add more precision on the details and according to recent paper, is made by the same mental region of the speech []. An extended meaning come also from gestures language for dumb people.
Gesture recognition got the attention of HCI researchers in order to find better ways to talk to the computer. The first one was the Hand Gestural Cursor (Put-That-There[]) aiming to the simplification of the means of communication between human and the machine.
Since then, the gesture definition included more techniques and got applied on the 2D recognition which is the multi-touch gestures.

@@

\section{Gestures Library}
We have analyzed some talk-shows in order to extract important gestures being performed, and defining a benchmark scenario. 
We have tried to target the following kinds of gestures in a first step:

\ignore{
(Get the Study from the report + pics + refs)
}

\png{handg}{Family of supported gestures}

@@

\section{Technical Aspects}
Pipeline of the work:
\png{pipeline}{Pipeline of work components}

\subsection{Used Material}
Technical aspects of the camera, and used framerate.

\ignore{
60 Hz, 640x480
}

@@

\subsection{Blob Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper. 
\ignore{
When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.
}
To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.

@@

\ignore{
\section{Simplified gesture generation}
Using these blocks we are able to perturb
}

@@

\section{Usability analysisn Naturelness and tests}

Naturelness came from the analysis of gestures used in talk shows.
(gesutures used many times means nature gestures)
Reverse thinking.

Usability in the context of RevTV ??
